---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# R Package  : 'dagnelie'

<!-- badges: start -->
<!-- badges: end -->

The goal of dagnelie is to provide a set of functions to use the allometric equations fitted by [Dagnelie et al. (2013)](http://hdl.handle.net/2268/155356)

Warning : This package is still under development.

Dagnelie et al proposed three form of tarif function, i.e. to predict the stem merchantable volume of a tree (stem section with girth < 22 cm, diameter < 7 cm) : 

The first equation predict the stem merchantable volume (in cubic meter) in response to tree girth measured at 1,3 meter (C130 in centimeter). The prediction of this equation can be obtained with `tarif1()`.

\[ v = b_0 + b_1*\mbox{C130} + b_2*\mbox{C130}^2 + b_3*\mbox{C130}^3 \]

The second equation predict the stem merchantable volume (in cubic meter) in response to tree girth measured at 1,3 meter (C130 in centimeter) and stand dominant height (HDOM in meter). The prediction of this equation can be obtained with `tarif2()`.

$$ v = b_0 + b_1*\mbox{C130} + b_2*\mbox{C130}^2 + b_3*\mbox{C130}^3 + b_4*\mbox{HDOM} + b_5*\mbox{C130}^2*\mbox{HDOM} $$

The third equation predict the stem merchantable volume (in cubic meter) in response to tree girth measured at 1,3 meter (C130 in centimeter) and tree height (H in meter). The prediction of this equation can be obtained with `tarif3()`.

\[ v = b_0 + b_1*\mbox{C130} + b_2*\mbox{C130}^2 + b_3*\mbox{C130}^3 + b_4*H + b_5*\mbox{C130}^2*H \]

Dagnelie et al. also proposed equation to convert girth measured at 1,5 m (Belgian style, C150) into C130. The prediction of this equation can be obtained with `C150toC130()`.

\[  \mbox{C130}= b_6*\mbox{C150} + b_7\]

The volume of merchandable branch can also be estimated with `tarif4()`function using the following equation : 

\[ v = c_0 + c_1 * \mbox{C130} + c_2 * \mbox{C130}^2 + c_3 * \mbox{C130}^3 \]

The parameters of these equations depends on the species and species codes have been set to use the equations in this package. You can get a table with species names and codes with `getSpeciesCodes()`.

Equation with parameters can been obtained with `getEquationWithParam()`.


## Installation

### Development version

You can install the development version of the package using the devtools package:

``` r
devtools::install_github("gauthierLigot/dagnelie")
```

### Other version

After downloading a version of the package (available on request), you can install it like so (let us suppose you stored in a "tmp" directory):

``` r
install.packages("c:/tmp/dagnelie_0.1.0.tar.gz", source = TRUE, repos=NULL)
```

## Example

The volume of a list of trees can be estimated as follows
```{r example}
library(dagnelie)

#get species codes
getSpeciesCodes()

# generate random data
trees<-data.frame(id = 1:10, species = rep(2,10), girth = 50:59)

# first equation applied on trees
tarif1(trees$girth,speciesCode = 2)
# second equation applied on trees
tarif2(trees$girth,hdom = 15,speciesCode = 2)
# third equation for one tree
tarif3(C130 = 50,height = 20,speciesCode = 2)
# volume of branches (vc22b)
tarif4(C130 = 50,speciesCode = 2)
```

